\title{Alessandro_Magnasco_Tech}
\documentclass[]{deedy-resume-openfont}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% READ FIRST %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Hello! I'm Ale, and this is my custom CV. I scripted it in LaTeX, a typesetting markup language.
% Thank you for visiting, and please don't hesitate to ask regarding any questions you may have.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\lastupdated

% generate title section
\namesection{Alessandro G.}{Magnasco}{
    %\vspace{-4pt}
    %\rule[5pt]{199pt}{1pt} \\ % 265 pt
    \urlstyle{same}\url{} 
    (Ale) :: he/him :: amagnasco at gradcenter.cuny.edu \\
    {\large << Experienced data scientist for critical infrastructure >>} \\
    %\rule[5pt]{400pt}{1pt} \\ % 445 pt
    \small{
    portfolio >> {tinyurl.com/amagnasco} :: github >> {amagnasco/cv} :: linkedin >> {/in/amagnasco} :: observable >> {@amagnasco}
    }
}
\vspace{5pt} 
\vspace{\topsep}

%\section{Interviewing for data scientist role}
\subsection{6 Years of experience managing critical data systems}
\vspace{\topsep}
    \begin{itemize}
        \item Master of Science in Data Analysis and Visualization, CUNY Graduate Center. \\
        >> Focus on non-standard statistical distributions, machine learning in Python and R \\
        >> Custom visualizations in D3.js, matplot, seaborn, ggplot, \TeX, Leaflet.js \\
        >> Doctoral coursework in demographic calculus and geographic theory
        \item Carried out the full-stack design and rollout of several new servers, databases, CRM systems, and websites.
        \item 7 years of experience managing DBs, including implementation and migration from other DBs \\ \textit{>> PostgreSQL, Salesforce, Airtable, various CRMs, various SQL-based}
        \item 4 years of experience managing ETL pipelines in Python and R, and machine learning (tidyverse, scikit-learn, pandas)
        \item 5 years of experience managing GIS pipelines, both static and dynamic, web and print
        \item FEMA-certified emergency manager for infrastructure; 3 years as supervisor for all phases of EM.
        %\item Google-certified in Advanced Data Analytics;  Social Justice Leader @ Transform Finance. % will complete by end of July
        \item Linux since 1998: RHEL, Ubuntu, Arch, Raspbian/Debian, Kali, Tails, Xen/Qubes; low-latency kernels; custom hw interfaces.
    \end{itemize}
\subsection{10 years of experience running core projects}
\vspace{\topsep}
    \begin{itemize} 
    	\item Designed and carried out to completion several mission-critical projects in different fields.
        \item Works closely with teams in the field to maximize efficiency.
        \item Managed company-wide purchasing for technology products and services.
        \item Experienced working with and managing 10s of Executive Boards, 100s of project teams, and 1000s general public.
        \item Reduced overhead costs when reconciling and auditing budgets of over US\$5,000,000.
	\end{itemize}

\section{Experience}
\runsubsection{Data Consultant}
\descript{>> American Red Cross and over 25 others }
\location{2012 -- ongoing >> North America, Caribbean, South America, Middle East}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
    \begin{itemize}
        \item @ Four universities, five startups, two dozen orgs on three different continents.
        \\>> Three years managing protected healthcare data (patient info) \& finance data (trading and ledgers)
        \\>> Six years managing environmental data (autecological and synecological) 
        \\RESULT: Multiple repeat clients, three international expansions, multiple successful launches
        \item Sole or lead administrator for three dozen systems, 4 server groups/3 LAMP stacks, and 6 CRM databases.
        \\ RESULT: >99.99\% uptime. No known breaches.
        \item Technical analysis and reporting on organizational data and infrastructure
        \\ RESULT: Authored plans reducing department IT expenses by >70\% and boosting client retention
        \\ RESULT: Same-day mitigation plan for >\$3M discovered privacy/cybersec exposure.
        \item Led assessments of data compliance (PCI, HIPAA, HUD, etc.)
        \\ RESULT: Created cross-referenced compliance plans for multiple frameworks.
        \item Deep embedding in multiple departments as needed for reporting capabilities
        \\ RESULT: 400\% increase in staff trained in data use and analysis
        \item Orchestrated analytics-driven design \& rollout of brand-new websites, servers, CRMs, and project management systems.
        \\ RESULT: Gave hundreds of technical and non-technical presentations to thousands of people
        \\ RESULT: Significantly scaled up Development operations, increasing productivity and revenue.
        \item Lead researcher, in charge of all internal analysis
        \\ >> Heavy, daily geostatistical analysis of various datasets on, for example, the entire population of NYC (n>8M)
        \\ RESULT: average 2-day data science turnaround allowed for quick decision-making
        \\ RESULT: created data analysis tools to cut manual analysis time down by >40,000x (1 week down to 5 min)
    \end{itemize}

% the following section is not compiled in the PDF
\iffalse

\section{Education}
    \runsubsection{Master of Science, Data Analysis \& Visualization}
        \descript{>> CUNY Graduate Center}
        \location{2021 -- 2023 >> New York, New York}
    \sectionsep
    \runsubsection{STEM Bachelor, Political Science \& IR}
        \descript{>> SUNY Geneseo}
        \location{2012 -- 2015 >> Geneseo, New York}
    \sectionsep
    \runsubsection{STEM Bachiller, Economics \& Business Management}
    	\descript{>> Vocational School}
        \location{2009 -- 2011 >> Mar del Plata, Argentina}
%\pagebreak

\section{SKILLS \& METRICS}
\begin{minipage}[t]{.5\textwidth}
    \subsection{System Administration}
		\textbullet{} Linux: Arch, Ubuntu, Fedora, Debian, Qubes, Tails, Whonix.\\
        \textbullet{} Significant experience with Mac/OS X and Windows. \\
   		\textbullet{} Desktops: Gnome (2, 3), Unity, KDE, LXDE, Xfce, Bash/shell. \\
    	\textbullet{} Networking: DHCP, routers, interference, cabling, iptables.\\
		\textbullet{} Security: Antiviral, rootkit, periferal, and social engineering.\\
        \textbullet{} Microcomputing and ARM systems. Xen. Docker.
    \sectionsep
	\subsection{DevOps}
   		\textbullet{} Implementing new IT systems, both software \& hardware.\\
       	\textbullet{} Installing and configuring OS, software, hardware. \\
        \textbullet{} Partitioning and disk recovery, through shell and GUI. \\
        \textbullet{} Managing kernel modules and boot options.\\
        \textbullet{} Technical crisis management, hotfixes and troubleshooting
    \sectionsep
   	\subsection{Scripting}
        \textbullet{} Data analysis: SQL, SPSS, R, Python (Pandas, Numpy) \\
        \textbullet{} Data serialization \& storage: JSON, YAML, CSV \\
        \textbullet{} Markup languages: \LaTeX, \XeLaTeX, HTML, Markdown 
    \sectionsep
    \subsection{Software}
        \textbullet{} CMS: WordPress and extensions, including CiviCRM \\
        \textbullet{} CRM: SalesForce, Raiser's Edge/Blackbaud, CiviCRM, others\\
        \textbullet{} Git, Bazaar, Screen, Asana, Overleaf, Slack.
\end{minipage}
\hfill
\begin{minipage}[t]{.45\textwidth}
    \subsection{Languages}
        \textbullet{} \location{Natively bilingual, English \& Spanish}
		\textbullet{} Reading comprehension in Italian \& Portuguese.\\
    %\vspace{-3pt}
    \sectionsep
	\subsection{Research}
    	\textbullet{} SPSS statistical analysis, GIS mapping \\
    	\textbullet{} Dossiers and analytics on prospects and key players \\
        \textbullet{} Market analysis, cost-benefit analyses \\
        \textbullet{} Legal research, startup, incorporation\\
    \sectionsep
     \subsection{Project Management}
        \textbullet{} Program design and evaluation.\\
		\textbullet{} Event planning and oversight.\\
        \textbullet{} Promotional design\\
        \textbullet{} Basic Analytics \\
        \textbullet{} Technical Documentation, reports\\
    \sectionsep
    \subsection{Budgeting \& Legal}
        \textbullet{} Official budgets and annual filings\\
        \textbullet{} Purchasing\\
		\textbullet{} Organizational by-laws\\
        \textbullet{} Transparency and compliance\\
        \textbullet{} Sarbanes-Oxley for nonprofits\\
		\textbullet{} Filing deadlines\\
        \textbullet{} Nonprofit tax exemptions\\
  	    \textbullet{} Auditing
    \sectionsep
\end{minipage}
\sectionsep
\sectionsep

\fi

\end{document}  \documentclass[]{article}